Constraint Grammar as a SAT problem

### 2015-06-01 paper/nodalida2015.tex
stuff

In the following sections, we report both execution time and
performance against state of the art.

>>>>

For evaluation, we measure the performance against the state of the
art CG parser VISL CG-3.
% both in terms of accuracy and execution time.
SAT-CG fares slightly worse for accuracy, and significantly worse for execution time.
The results are presented in more detail in the following sections.
